---
title: "Data Journalism: 2020 Campaign Events by Candidate and State"
description: |
  Here's an analysis showing the presidential candidates with the most campaign events during the 2020 election, in addition to a breakdown of the top 5 states where candidates hosted the most events.
author:
  - name: Steph Gemmell
    url: 
date: 04-13-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(janitor)
library(glue)
library(plotly)
library(DT)
library(kableExtra)
library(htmlwidgets)
library(htmltools)
```


Candidates with the most campaign events
=====================================
Pete Buttigieg, Elizabeth Warren, Amy Klobuchar, Bernie Sanders, and Beto O'Rourke hosted the most campaign events leading up to the 2020 presidential election.

```{r}
fig <- plot_ly(
  x = c("Buttigieg", "Warren", "Klobuchar", "Sanders", "O'Rourke"),
  y = c(74, 73, 70, 67, 64),
  type = "bar",
  color = "orange"
)
fig <- fig %>% layout(title = "Candidates with Most Campaign Events",
         xaxis = list(title = "Candidate"),
         yaxis = list (title = "Number of Campaign Events"))

fig
```

States hosting the most campaign events
=====================================
Iowa, New Hampshire, South Carolina, Washington, DC, and California were the five most popular locations for 2020 presidential candidates' campaign events. 
(Percentages based on data for the top 5 states only)

```{r}
State <- c("IA", "NH", "SC", "DC", "CA")
EventNumber <- c(200, 132, 90, 86, 69)
df <- data.frame(State, EventNumber)
fig <- df %>% plot_ly(labels = ~State, values = ~EventNumber)
fig <- fig %>% add_pie(hole = 0.6)
fig <- fig %>% layout(
                  title = "States hosting the most campaign events",  showlegend = F,
                  xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                  yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig
```