---
title: "Data Journalism: Consumer Complaints - Untimely Responses"
description: |
  Here's an analysis of consumer complaints from March 2020 to December 2020 that did not receive timely responses. 
  Source: Consumer Financial Protection Bureau
author:
  - name: Steph Gemmell
    url: {}
date: 04-13-2021
output:
  distill::distill_article:
    self_contained: false
categories:
  - research
  - smpa
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(janitor)
library(glue)
library(plotly)
library(DT)
library(kableExtra)
library(htmlwidgets)
library(htmltools)
```

Product Categories
=====================================
Out of more than 390,000 consumer complaints, just under 1 percent did not receive a timely response. I isolated the data on these complaints to investigate the product categories that most frequently prompted complaints and failed to provide timely responses.
Among the complaints that did not receive a timely response, the top five product categories involved were:

```{r}
Products <- c('Credit reporting or repair','Debt collection','Credit card or prepaid card','Mortgage','Checking or savings account')
Incidences <- c(255748,46088,29128,20940,20679)
df <- data.frame(Products, Incidences)
fig <- df %>% plot_ly(labels = ~Products, values = ~Incidences)
fig <- fig %>% add_pie(hole = 0.6)
fig <- fig %>% layout(
                  title = "Products Involved in Complaints with Untimely Responses",  showlegend = F,
                  xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                  yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig
```

Company Responses
=====================================
The results consumers received in cases where the company failed to provide a timely response included:

```{r}
fig <- plot_ly(
  x = c("Closed with explanation","Untimely response","Closed with non-monetary relief","Closed with monetary relief"),
  y = c(2550,1129,66,61),
  type = "bar",
  color = "orange"
)
fig <- fig %>% layout(title = "Company Responses to Consumers",
         xaxis = list(title = "Response"),
         yaxis = list (title = "Number of Occurrences"))

fig
```

Companies
=====================================
The 10 companies that failed to provide timely responses to consumer complaints most frequently included:

```{r}
fig <- plot_ly(
  x = c("Xerox State & Local Solutions, Inc.","Army and Air Force Exchange Service","Lending Club Corp","Atlanticus Services Corporation","MoneyLion Inc.","Carter-Young, Inc.","WAKEFIELD & ASSOCIATES, INC.","WELLS FARGO & COMPANY","AmerAssist A/R Solutions, Inc.","Capital Accounts, LLC"),
  y = c(413,85,84,68,64,61,56,54,52,51),
  type = "bar",
  color = "orange"
)
fig <- fig %>% layout(title = "Companies Providing Most Untimely Responses",
         xaxis = list(title = "Companies"),
         yaxis = list (title = "Number of Unitmely Responses"))

fig
```
```



